HGIS Pendleton Carbonates

### 2021-10-08 R/HGIS_pendleton_all.Rmd
Playing with Bchron for calibration
reformat age-depth plot

options(digits = 4)
options(scipen = 3)
```

@@

```{r}
combined_results %>% 
  filter(sample_name != "6:7_39-40") %>% 
ggplot(aes(depth, rc_age, color = method)) +
  geom_pointrange(aes(ymin = rc_age - sig_rc_age, 
                      ymax = rc_age + sig_rc_age),
                  size = 0.5) +
  geom_smooth() +
  ggtitle("Age vs depth for graphite and HGIS")
```

@@

>>>>

options(digits = 4)
options(scipen = 3)
theme_set(theme_classic())
```

@@

```{r}
combined_results %>% 
  filter(sample_name != "6:7_39-40") %>% 
ggplot(aes(depth, rc_age, color = method)) +
  geom_pointrange(aes(ymin = rc_age - sig_rc_age, 
                      ymax = rc_age + sig_rc_age),
                  size = 0.5) +
  geom_smooth() +
  coord_flip() +
  scale_y_reverse() +
  scale_x_reverse() +
  ggtitle("Age vs depth for graphite and HGIS")
```

@@

Trying Bchron here instead. Use is a bit friendlier in Rmarkdown.

```{r}
library(Bchron)

cal_sub <- combined_results %>% 
  filter(rc_age > 0) %>% 
  mutate(id = paste(sample_name, "-", method)) %>% 
  select(id, depth, rc_age, sig_rc_age)

cal_dates <- with(cal_sub,
  BchronCalibrate(rc_age, sig_rc_age, positions = depth, ids = id))
plot(cal_dates)
```
